% Bibliografía manual (compatible con tectonic). Para la versión APA oficial con
% biblatex+biber, ver la nota en settings.tex y usar thesisRefs.bib.
\begin{thebibliography}{99}
\addcontentsline{toc}{chapter}{Referencias}

\bibitem{polymarket_prices}
Polymarket Documentation. \textit{Prices \& Orderbooks.}
\url{https://docs.polymarket.com/polymarket-learn/trading/using-the-orderbook}

\bibitem{polymarket_trading}
Polymarket Documentation. \textit{Order Lifecycle.}
\url{https://docs.polymarket.com/concepts/order-lifecycle}

\bibitem{wolfers2004prediction}
Wolfers, J., \& Zitzewitz, E. (2004). Prediction Markets.
\textit{Journal of Economic Perspectives, 18}(2), 107--126.

\bibitem{zhang2019deeplob}
Zhang, Z., Zohren, S., \& Roberts, S. (2019). DeepLOB: Deep Convolutional Neural
Networks for Limit Order Books. \textit{IEEE Transactions on Signal Processing,
67}(11), 3001--3012.

\bibitem{ntakaris2018}
Ntakaris, A., Magris, M., Kanniainen, J., Gabbouj, M., \& Iosifidis, A. (2018).
Benchmark dataset for mid-price forecasting of limit order book data with machine
learning methods. \textit{Journal of Forecasting, 37}(8), 852--866.

\bibitem{tsantekidis2017}
Tsantekidis, A., Passalis, N., Tefas, A., Kanniainen, J., Gabbouj, M., \& Iosifidis, A.
(2017). Using deep learning to detect price change indications in financial markets.
\textit{European Signal Processing Conference (EUSIPCO)}.

\bibitem{sirignano2019universal}
Sirignano, J., \& Cont, R. (2019). Universal features of price formation in financial
markets: perspectives from deep learning. \textit{Quantitative Finance, 19}(9), 1449--1459.

\bibitem{jha2020digital}
Jha, R., et al. (2020). Deep Learning for Digital Asset Limit Order Books.
\textit{arXiv:2010.01241}.

\bibitem{kearns2013}
Kearns, M., \& Nevmyvaka, Y. (2013). Machine Learning for Market Microstructure and
High Frequency Trading. In \textit{High Frequency Trading: New Realities for Traders,
Markets and Regulators}.

\bibitem{gu2020empirical}
Gu, S., Kelly, B., \& Xiu, D. (2020). Empirical Asset Pricing via Machine Learning.
\textit{The Review of Financial Studies, 33}(5), 2223--2273.

\bibitem{lopezdeprado2018}
López de Prado, M. (2018). \textit{Advances in Financial Machine Learning}. Wiley.

\bibitem{bailey2014deflated}
Bailey, D. H., \& López de Prado, M. (2014). The Deflated Sharpe Ratio: Correcting for
Selection Bias, Backtest Overfitting, and Non-Normality. \textit{The Journal of
Portfolio Management, 40}(5), 94--107.

\bibitem{sun2016coral}
Sun, B., Feng, J., \& Saenko, K. (2016). Return of Frustratingly Easy Domain Adaptation.
\textit{AAAI Conference on Artificial Intelligence}.

\bibitem{lim2021tft}
Lim, B., Arik, S. O., Loeff, N., \& Pfister, T. (2021). Temporal Fusion Transformers for
Interpretable Multi-horizon Time Series Forecasting. \textit{International Journal of
Forecasting, 37}(4), 1748--1764.

\bibitem{sculley2015debt}
Sculley, D., et al. (2015). Hidden Technical Debt in Machine Learning Systems.
\textit{Advances in Neural Information Processing Systems (NeurIPS)}.

\end{thebibliography}
